### 2015-05-10 thesis/thesis/chap4/chap4.tex
changes

In this section, the objective is to investigate the effectiveness of the proposed strategic system.
We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive).
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.

>>>>

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives. 
%These entities are developed with respect to what is explained in Section \ref{s4:Preliminaries}. 
In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies.

The simulation application is written in
\textit{C\#} using \textit{Visual Studio}. We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory. Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.  We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses. The request contains the flight dates, the origin and destination, type of tickets, and number of guests. The response contains different flights with different companies, prices, timing, etc. A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.
The dataset records the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and \textit{reliability} \cite{Almasri}.

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive).
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.
